# Developing Data Scientists: Exploring Free Code Camp's ["2016 New Coder Survey"](https://www.kaggle.com/freecodecamp/2016-new-coder-survey-)
#### By [David Venturi](http://davidventuri.com/)

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(countrycode)
library(plyr)
library(dplyr)
library(ggthemes)
library(scales)
library(grid)
library(gridExtra)
library(extrafont)
library(extrafontdb)
library(tidyr)
library(stringr)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
setwd('~/Documents/CS/DAND/udacity-dand/p4')
fcc <- read.csv('2016-FCC-New-Coders-Survey-Data.csv')

# Create new continent variables and move them to their alphabetical position
fcc$ContinentCitizen <- countrycode(fcc$CountryCitizen, 'country.name', 'continent')
fcc$ContinentLive <- countrycode(fcc$CountryLive, 'country.name', 'continent')
fcc <- select(fcc, Age:CountryCitizen, ContinentCitizen, CountryLive, ContinentLive, EmploymentField:StudentDebtOwe)

# 66 countries with no assigned continent via countrycode()
cit_live_cols <- select(fcc, CountryCitizen:ContinentLive)
problem_countries <- with(cit_live_cols, cit_live_cols[(!is.na(CountryCitizen) & is.na(ContinentCitizen)) | (!is.na(CountryLive) & is.na(ContinentLive)), ])

# Problem country/continent names
fix_cont <- c('Africa', 'Asia', 'Europe', 'Europe', 'Europe', 'Oceania')
names(fix_cont) <- c('Nambia', 'Taiwan', 'Canary Islands', 'Kosovo', 'Channel Islands', 'Hawaii')
# "Hawaii is generally included in Oceania, even though it is a part of the United States" http://cs.mcgill.ca/~rwest/wikispeedia/wpcd/wp/o/Oceania.htm

# Assign continents to problem countries
fcc$ContinentCitizen <- ifelse(fcc$CountryCitizen %in% names(fix_cont), fix_cont[as.character(fcc$CountryCitizen)], fcc$ContinentCitizen)
fcc$ContinentLive <- ifelse(fcc$CountryLive %in% names(fix_cont), fix_cont[as.character(fcc$CountryLive)], fcc$ContinentLive)

# South American countries in dataset
s_america <- c('Argentina', 'Bolivia', 'Brazil', 'Chile', 'Colombia', 'Ecuador', 'Guyana', 'Netherland Antilles', 'Paraguay', 'Peru', 'Uruguay', 'Venezuela')

# Separate Americas into North and South
make_s_america <- function(continent, country) {
  return(ifelse(continent == 'Americas' & country %in% s_america, 'South America', continent))
}

make_n_america <- function(continent, country) {
  return(ifelse(continent == 'Americas' & !(country %in% s_america), 'North America', continent))
}

fcc$ContinentCitizen <- make_s_america(fcc$ContinentCitizen, fcc$CountryCitizen)
fcc$ContinentCitizen <- make_n_america(fcc$ContinentCitizen, fcc$CountryCitizen)
fcc$ContinentLive <- make_s_america(fcc$ContinentLive, fcc$CountryLive)
fcc$ContinentLive <- make_n_america(fcc$ContinentLive, fcc$CountryLive)

# TEST CONTINENT VARS
# table(fcc$ContinentLive)
# table(fcc$ContinentCitizen)

# Make continents factor variables
fcc$ContinentCitizen <- factor(fcc$ContinentCitizen)
fcc$ContinentLive <- factor(fcc$ContinentLive)

# Fix Netherlands (Country...)
fcc$CountryCitizen <- ifelse(fcc$CountryCitizen == "Netherlands (Holland, Europe)", "Netherlands", as.character(fcc$CountryCitizen))
fcc$CountryLive <- ifelse(fcc$CountryLive == "Netherlands (Holland, Europe)", "Netherlands", as.character(fcc$CountryLive))
fcc$CountryCitizen <- factor(fcc$CountryCitizen)
fcc$CountryLive <- factor(fcc$CountryLive)

# Fix Math/Mathematics (SchoolMajor)
fcc$SchoolMajor <- ifelse(fcc$SchoolMajor == "Math", "Mathematics", as.character(fcc$SchoolMajor))
fcc$SchoolMajor <- factor(fcc$SchoolMajor)
table(fcc_data$SchoolMajor)
```

## Full Dataset
The original survey dataset consists of 113 variables. Most of these variables are answers to survey questions, though a few are computer-generated (e.g. respondent ID and survey start/end times). **Over 15,000 observations** (i.e. respondents) exist.

I created two new variables, *ContinentCitizen* and *ContinentLive*, for a new total of **115 variables**.

```{r echo=FALSE, Full_Dataset}
dim(fcc)
```

The [```str``` function](http://www.r-bloggers.com/str-implementation-for-data-frames/) output is long and messy, so I won't print it here. Please consult Free Code Camp's [list of survey questions and possible answers](https://github.com/FreeCodeCamp/2016-new-coder-survey/blob/master/survey-data-dictionary.md).

## Data Science Subset
646 respondents answered "*Data Scientist/Data Engineer*" to the question: "*Which one of these roles are you most interested in?*"

```{r echo=FALSE, DS_Dataset}
# "Which one of these roles are you most interested in?"
fcc_data <- with(fcc, fcc[JobRoleInterest == '  Data Scientist / Data Engineer' & !is.na(JobRoleInterest), ])
dim(fcc_data)
```

## Univariate Plots Section
```{r echo=FALSE, Univariate_Plots}
# Order factor based on the survey's data science subset results (ascending)
order_factor <- function(fcc_data_var) {
  table(fcc_data_var)
  var_table <- table(fcc_data_var)
  var_levels <- names(var_table)[order(var_table)]
  return(factor(fcc_data_var, levels = var_levels))
}

# Pretty bar chart
nice_bar_plot <- function(col, question, num_answers, lab_size, lab_cut) {
  df <- as.data.frame(col)
  colnames(df)[1] <- "x"
  
  title.grob <- textGrob(
    label = paste(question, sep=" "),
    x = unit(0.3, "lines"), 
    y = unit(-0.3, "lines"),
    hjust = 0, vjust = 0,
    gp = gpar(fontsize = 16, fontface="bold"))
  
  dfTab <- as.data.frame(table(df))
  colnames(dfTab)[1] <- "x"
  
  dfTab$lab <- 100 * dfTab$Freq / num_answers
  dfTab$lab <- ifelse(dfTab$lab >= lab_cut, sprintf("%1.1f%%", dfTab$lab), "")
  dfTab$lab <- as.character(dfTab$lab)
  
  plot <- ggplot(df) +
    geom_bar(aes(x), color="#02b3e4", fill="#02b3e4") +
    theme_minimal() +
    scale_x_discrete(drop=FALSE) +
    labs(title="", x=NULL, y=paste(as.character(num_answers), "out of 646 developing data scientists/engineers answered")) +
    theme(axis.text=element_text(size=10),
          axis.title.x=element_text(colour="#02b3e4", margin=margin(15,0,9,0))) +
    geom_text(data=dfTab, aes(x=x,y=Freq,label=lab), hjust = 1,
              color="white", size=lab_size, fontface=2) +
    coord_flip()
  
  plot <- arrangeGrob(plot, top = title.grob)
  return(plot)
}

# LEARNER GOALS AND APPROACHES

# JobPref
fcc_data$JobPref <- order_factor(fcc_data$JobPref)
job_pref_na_rm <- with(fcc_data, fcc_data[!is.na(JobPref), ])
g_job_pref <- grid.arrange(nice_bar_plot(job_pref_na_rm$JobPref, "Would you prefer to...", nrow(job_pref_na_rm), 7, 0))
g_job_pref
ggsave(file="JobPref.png", g_job_pref)

# JobApplyWhen
fcc_data$JobApplyWhen <- order_factor(fcc_data$JobApplyWhen)
job_apply_when_na_rm <- with(fcc_data, fcc_data[!is.na(JobApplyWhen), ])
g_job_apply_when <- grid.arrange(nice_bar_plot(job_apply_when_na_rm$JobApplyWhen, "When do you plan to start applying for jobs?", nrow(job_apply_when_na_rm), 7, 0))
g_job_apply_when
ggsave(file="JobApplyWhen.png", g_job_apply_when)

# JobWherePref
fcc_data$JobWherePref <- order_factor(fcc_data$JobWherePref)
job_where_pref_na_rm <- with(fcc_data, fcc_data[!is.na(JobWherePref), ])
g_job_where_pref <- grid.arrange(nice_bar_plot(job_where_pref_na_rm$JobWherePref, "Would you prefer to work...", nrow(job_where_pref_na_rm), 9, 0))
g_job_where_pref
ggsave(file="JobWherePref.png", g_job_where_pref)

# JobRelocateYesNo
levels(fcc_data$JobRelocateYesNo)[levels(fcc_data$JobRelocateYesNo)=="0"] <- "No"
levels(fcc_data$JobRelocateYesNo)[levels(fcc_data$JobRelocateYesNo)=="1"] <- "Yes"
fcc_data$JobRelocateYesNo <- order_factor(fcc_data$JobRelocateYesNo)
job_relo_na_rm <- with(fcc_data, fcc_data[!is.na(JobRelocateYesNo), ])
g_job_relo <- grid.arrange(nice_bar_plot(job_relo_na_rm$JobRelocateYesNo, "Are you willing to relocate for a job?", nrow(job_relo_na_rm), 9, 0))
g_job_relo
ggsave(file="JobRelocateYesNo.png", g_job_relo)

# LEARN TO USE LAZYEVAL TO MAKE A FUNCTION FOR THE NEXT THREE WRANGLING SEQUENCES (CodeEvent, Resource, Podcast) IN THE FUTURE

# CodeEvent
code_event_cols <- select(fcc_data, CodeEventBootcamp:CodeEventWorkshop)
code_event_cols$CodeEventOther <-
  ifelse(!is.na(code_event_cols$CodeEventOther),
         as.integer(1), NA)
code_event_cols$answered <-
  ifelse(rowSums(code_event_cols, na.rm = TRUE) != 0, 1, 0)
num_answers_code_event <- sum(code_event_cols[,'answered'])
code_event_sum <- code_event_cols %>% summarise_each(funs(sum(., na.rm=TRUE)))
code_event_sum_long <- gather(code_event_sum, event, num_yes, CodeEventBootcamp:CodeEventWorkshop) %>%
  arrange(desc(num_yes)) %>%
  mutate(event = str_sub(event, nchar("CodeEvent") + 1, -1))
code_event_factor <- as.data.frame(rep(code_event_sum_long$event,
                                       code_event_sum_long$num_yes))
colnames(code_event_factor) <- "event"
code_event_factor$event <- order_factor(code_event_factor$event)
g_code_event <- grid.arrange(nice_bar_plot(code_event_factor$event, "Which types of in-person coding events have you attended?", num_answers_code_event, 3.5, 2.9))
g_code_event
ggsave(file="CodeEvent.png", g_code_event)

# Resource
resource_cols <- select(fcc_data, ResourceBlogs:ResourceYouTube)
resource_cols$ResourceOther <- ifelse(!is.na(resource_cols$ResourceOther), as.integer(1), NA)
resource_cols$answered <- ifelse(rowSums(resource_cols, na.rm = TRUE) != 0, 1, 0)
num_answers_resource <- sum(resource_cols[,'answered'])
resource_sum <- resource_cols %>% summarise_each(funs(sum(., na.rm=TRUE)))
resource_sum_long <- gather(resource_sum, resource, num_yes, ResourceBlogs:ResourceYouTube) %>%
  arrange(desc(num_yes)) %>%
  mutate(resource = str_sub(resource, nchar("Resource") + 1, -1))
resource_factor <- as.data.frame(rep(resource_sum_long$resource,
                                       resource_sum_long$num_yes))
colnames(resource_factor) <- "resource"
resource_factor$resource <- order_factor(resource_factor$resource)
g_resource <- grid.arrange(nice_bar_plot(resource_factor$resource, "Which learning resources have you found helpful?", num_answers_resource, 3.5, 1.5))
g_resource
ggsave(file="Resource.png", g_resource)

# Podcast
podcast_cols <- select(fcc_data, PodcastChangeLog:PodcastWebAhead)
podcast_cols$PodcastOther <- ifelse(!is.na(podcast_cols$PodcastOther), as.integer(1), NA)
podcast_cols$answered <- ifelse(rowSums(podcast_cols, na.rm = TRUE) != 0, 1, 0)
num_answers_podcast <- sum(podcast_cols[,'answered'])
podcast_sum <- podcast_cols %>% summarise_each(funs(sum(., na.rm=TRUE)))
podcast_sum_long <- gather(podcast_sum, podcast, num_yes, PodcastChangeLog:PodcastWebAhead) %>%
  arrange(desc(num_yes)) %>%
  mutate(podcast = str_sub(podcast, nchar("Podcast") + 1, -1))
podcast_factor <- as.data.frame(rep(podcast_sum_long$podcast,
                                       podcast_sum_long$num_yes))
colnames(podcast_factor) <- "podcast"
podcast_factor$podcast <- order_factor(podcast_factor$podcast)
g_podcast <- grid.arrange(nice_bar_plot(podcast_factor$podcast, "Which coding-related podcasts have you found helpful?", num_answers_podcast, 3.5, 7))
g_podcast
ggsave(file="podcast.png", g_podcast)

# Bootcamp
fcc_data$BootcampName <- order_factor(fcc_data$BootcampName)
bootcamp_name_na_rm <- with(fcc_data, fcc_data[!is.na(BootcampName), ])
g_bootcamp_name <- grid.arrange(nice_bar_plot(droplevels(bootcamp_name_na_rm$BootcampName), "If you have attended a full-time coding bootcamp, which one?", nrow(bootcamp_name_na_rm), 4, 0))
g_bootcamp_name
ggsave(file="BootcampName.png", g_bootcamp_name)

# DEMOGRAPHICS

# ContinentCitizen
fcc_data$ContinentCitizen <- order_factor(fcc_data$ContinentCitizen)
continent_citizen_na_rm <- with(fcc_data, fcc_data[!is.na(ContinentCitizen), ])
g_continent_citizen <- grid.arrange(nice_bar_plot(droplevels(continent_citizen_na_rm$ContinentCitizen), "Which continent are you a citizen of?", nrow(continent_citizen_na_rm), 4, 4))
g_continent_citizen
ggsave(file="ContinentCitizen.png", g_continent_citizen)

# CountryCitizen
fcc_data$CountryCitizen <- order_factor(fcc_data$CountryCitizen)
country_citizen_na_rm <- with(fcc_data, fcc_data[!is.na(CountryCitizen), ])
country_citizen_na_rm_lim <- country_citizen_na_rm %>% group_by(CountryCitizen) %>% filter(n() > 4)
g_country_citizen <- grid.arrange(nice_bar_plot(droplevels(country_citizen_na_rm_lim$CountryCitizen), "Which country are you a citizen of?", nrow(country_citizen_na_rm), 2.5, 3))
g_country_citizen
ggsave(file="CountryCitizen.png", g_country_citizen)

# CountryLive
# fcc_data$CountryLive <- order_factor(fcc_data$CountryLive)
# country_live_na_rm <- with(fcc_data, fcc_data[!is.na(CountryLive), ])
# country_live_na_rm_lim <- country_live_na_rm %>% group_by(CountryLive) %>% filter(n() > 4)
# g_country_live <- grid.arrange(nice_bar_plot(droplevels(country_live_na_rm_lim$CountryLive), "Which country do you currently live in?", nrow(country_live_na_rm), 2.5, 3))
#g_country_live
# ggsave(file="CountryLive.png", g_country_live)

# CityPopulation
fcc_data$CityPopulation <- order_factor(fcc_data$CityPopulation)
city_pop_na_rm <- with(fcc_data, fcc_data[!is.na(CityPopulation), ])
g_city_pop <- grid.arrange(nice_bar_plot(city_pop_na_rm$CityPopulation, "About how many people live in your city?", nrow(city_pop_na_rm), 9, 0))
g_city_pop
ggsave(file="CityPopulation.png", g_city_pop)

# Ethnic Minority
levels(fcc_data$IsEthnicMinority)[levels(fcc_data$IsEthnicMinority)=="0"] <- "No"
levels(fcc_data$IsEthnicMinority)[levels(fcc_data$IsEthnicMinority)=="1"] <- "Yes"
fcc_data$IsEthnicMinority <- order_factor(fcc_data$IsEthnicMinority)
ethnic_minority_na_rm <- with(fcc_data, fcc_data[!is.na(IsEthnicMinority), ])
g_ethnic_minority <- grid.arrange(nice_bar_plot(ethnic_minority_na_rm$IsEthnicMinority, "Are you an ethnic minority in your country?", nrow(ethnic_minority_na_rm), 9, 0))
g_ethnic_minority
ggsave(file="IsEthnicMinority.png", g_ethnic_minority)

# LanguageAtHome
fcc_data$LanguageAtHome <- order_factor(fcc_data$LanguageAtHome)
language_na_rm <- with(fcc_data, fcc_data[!is.na(LanguageAtHome), ])
language_na_rm_lim <- language_na_rm %>% group_by(LanguageAtHome) %>% filter(n() > 5)
g_language <- grid.arrange(nice_bar_plot(droplevels(language_na_rm_lim$LanguageAtHome), "Which language do you speak at home with your family?", nrow(language_na_rm), 3, 3))
g_language
ggsave(file="LanguageAtHome.png", g_language)

# SchoolDegree
fcc_data$SchoolDegree <- order_factor(fcc_data$SchoolDegree)
school_degree_na_rm <- with(fcc_data, fcc_data[!is.na(SchoolDegree), ])
g_school_degree <- grid.arrange(nice_bar_plot(school_degree_na_rm$SchoolDegree, "What's the highest degree of level of school you have completed?", nrow(school_degree_na_rm), 3.5, 4))
g_school_degree
ggsave(file="SchoolDegree.png", g_school_degree)

# SchoolMajor
fcc_data$SchoolMajor <- order_factor(fcc_data$SchoolMajor)
school_major_na_rm <- with(fcc_data, fcc_data[!is.na(SchoolMajor), ])
school_major_na_rm_lim <- school_major_na_rm %>% group_by(SchoolMajor) %>% filter(n() > 5)
g_school_major <- grid.arrange(nice_bar_plot(droplevels(school_major_na_rm_lim$SchoolMajor), "What was the main subject your studied in university?", nrow(school_major_na_rm), 3, 0))
g_school_major
ggsave(file="SchoolMajor.png", g_school_major)

# EmploymentStatus
fcc_data$EmploymentStatus <- order_factor(fcc_data$EmploymentStatus)
employment_status_na_rm <- with(fcc_data, fcc_data[!is.na(EmploymentStatus), ])
g_employment_status <- grid.arrange(nice_bar_plot(employment_status_na_rm$EmploymentStatus, "Regarding employment status, are you currently...", nrow(employment_status_na_rm), 3.5, 4))
g_employment_status
ggsave(file="EmploymentStatus.png", g_employment_status)

# EmploymentField
fcc_data$EmploymentField <- as.character(fcc_data$EmploymentField)
# Change "NA" to "other" if respondent provided EmploymentFieldOther
fcc_data$EmploymentField <- with(fcc_data, ifelse(is.na(EmploymentField) & !is.na(EmploymentFieldOther), 'other', EmploymentField))
fcc_data$EmploymentField <- as.factor(fcc_data$EmploymentField)

fcc_data$EmploymentField <- order_factor(fcc_data$EmploymentField)
employment_field_na_rm <- with(fcc_data, fcc_data[!is.na(EmploymentField), ])
g_employment_field <- grid.arrange(nice_bar_plot(droplevels(employment_field_na_rm$EmploymentField), "Which field do you work in?", nrow(employment_field_na_rm), 3.5, 2))
g_employment_field
ggsave(file="EmploymentField.png", g_employment_field)
```

## Univariate Analysis

# Change levels 0 > no, 1>yes for fcc and not fcc_data?

#### What is the structure of your dataset?

#### What is/are the main feature(s) of interest in your dataset?

#### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?

#### Did you create any new variables from existing variables in the dataset?

#### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?



## Bivariate Plots Section
```{r echo=FALSE, Bivariate_Plots}

```

## Bivariate Analysis

#### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

#### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

#### What was the strongest relationship you found?




## Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

```

## Multivariate Analysis

#### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

#### Were there any interesting or surprising interactions between features?

#### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

------

## Final Plots and Summary

#### Plot One
```{r echo=FALSE, Plot_One}

```

#### Description One


#### Plot Two
```{r echo=FALSE, Plot_Two}

```

#### Description Two


#### Plot Three
```{r echo=FALSE, Plot_Three}

```

#### Description Three

------

## Reflection
