# Developing Data Scientists: Exploring Free Code Camp's ["2016 New Coder Survey"](https://www.kaggle.com/freecodecamp/2016-new-coder-survey-)
#### By [David Venturi](http://davidventuri.com/)

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(countrycode)
library(plyr)
library(dplyr)
library(ggthemes)
library(scales)
library(grid)
library(gridExtra)
library(extrafont)
library(extrafontdb)
library(tidyr)
library(stringr)
```

```{r echo=FALSE, Load_Clean_the_Data}
# Load the Data
setwd('~/Documents/CS/DAND/udacity-dand/p4')
fcc <- read.csv('2016-FCC-New-Coders-Survey-Data.csv')

# Create new continent variables and move them to their alphabetical position
fcc$ContinentCitizen <- countrycode(fcc$CountryCitizen, 'country.name', 'continent')
fcc$ContinentLive <- countrycode(fcc$CountryLive, 'country.name', 'continent')
fcc <- select(fcc, Age:CountryCitizen, ContinentCitizen, CountryLive, ContinentLive, EmploymentField:StudentDebtOwe)

# Clean the data

# 66 countries with no assigned continent via countrycode()
cit_live_cols <- select(fcc, CountryCitizen:ContinentLive)
problem_countries <- with(cit_live_cols, cit_live_cols[(!is.na(CountryCitizen) & is.na(ContinentCitizen)) | (!is.na(CountryLive) & is.na(ContinentLive)), ])

# Problem country/continent names
fix_cont <- c('Africa', 'Asia', 'Europe', 'Europe', 'Europe', 'Oceania')
names(fix_cont) <- c('Nambia', 'Taiwan', 'Canary Islands', 'Kosovo', 'Channel Islands', 'Hawaii')
# "Hawaii is generally included in Oceania, even though it is a part of the United States" http://cs.mcgill.ca/~rwest/wikispeedia/wpcd/wp/o/Oceania.htm

# Assign continents to problem countries
fcc$ContinentCitizen <- ifelse(fcc$CountryCitizen %in% names(fix_cont), fix_cont[as.character(fcc$CountryCitizen)], fcc$ContinentCitizen)
fcc$ContinentLive <- ifelse(fcc$CountryLive %in% names(fix_cont), fix_cont[as.character(fcc$CountryLive)], fcc$ContinentLive)

# South American countries in dataset
s_america <- c('Argentina', 'Bolivia', 'Brazil', 'Chile', 'Colombia', 'Ecuador', 'Guyana', 'Netherland Antilles', 'Paraguay', 'Peru', 'Uruguay', 'Venezuela')

# Separate Americas into North and South
make_s_america <- function(continent, country) {
  return(ifelse(continent == 'Americas' & country %in% s_america, 'South America', continent))
}

make_n_america <- function(continent, country) {
  return(ifelse(continent == 'Americas' & !(country %in% s_america), 'North America', continent))
}

fcc$ContinentCitizen <- make_s_america(fcc$ContinentCitizen, fcc$CountryCitizen)
fcc$ContinentCitizen <- make_n_america(fcc$ContinentCitizen, fcc$CountryCitizen)
fcc$ContinentLive <- make_s_america(fcc$ContinentLive, fcc$CountryLive)
fcc$ContinentLive <- make_n_america(fcc$ContinentLive, fcc$CountryLive)

# TEST CONTINENT VARS
# table(fcc$ContinentLive)
# table(fcc$ContinentCitizen)

# Make continents factor variables
fcc$ContinentCitizen <- factor(fcc$ContinentCitizen)
fcc$ContinentLive <- factor(fcc$ContinentLive)

# Fix Netherlands (Country...)
fcc$CountryCitizen <- ifelse(fcc$CountryCitizen == "Netherlands (Holland, Europe)", "Netherlands", as.character(fcc$CountryCitizen))
fcc$CountryLive <- ifelse(fcc$CountryLive == "Netherlands (Holland, Europe)", "Netherlands", as.character(fcc$CountryLive))
fcc$CountryCitizen <- factor(fcc$CountryCitizen)
fcc$CountryLive <- factor(fcc$CountryLive)

# Fix Math/Mathematics (SchoolMajor)
fcc$SchoolMajor <- ifelse(fcc$SchoolMajor == "Math", "Mathematics", as.character(fcc$SchoolMajor))
fcc$SchoolMajor <- factor(fcc$SchoolMajor)

# Change 0 to No, 1 to Yes for two plots
fcc$JobRelocateYesNo <- factor(fcc$JobRelocateYesNo)
fcc$JobRelocateYesNo <- revalue(fcc$JobRelocateYesNo, c("0"="No", "1"="Yes"))
fcc$IsEthnicMinority <- factor(fcc$IsEthnicMinority)
fcc$IsEthnicMinority <- revalue(fcc$IsEthnicMinority, c("0"="No", "1"="Yes"))

# Add two data science podcast columns
fcc$PodcastPartiallyDerivative <- with(fcc, ifelse(PodcastOther == "Partially Derivative" | PodcastOther == "http://www.partiallyderivative.com/", as.integer(1), NA))
fcc$PodcastBecomingDataSci <- with(fcc, ifelse(PodcastOther == "Becoming A Data Scientist" | PodcastOther == "Learning to be a Data Scientist", as.integer(1), NA))
fcc$PodcastTalkingMachines <- with(fcc, ifelse(PodcastOther == "Talking machines", as.integer(1), NA))
fcc <- select(fcc, Age:PodcastOther, PodcastPartiallyDerivative:PodcastTalkingMachines, PodcastProgrammingThrowDown:StudentDebtOwe)

# Change "NA" to "other" for EmploymentStatus if respondent provided EmploymentStatusOther
fcc$EmploymentStatus <- as.character(fcc$EmploymentStatus)
fcc$EmploymentStatus <- with(fcc, ifelse(is.na(EmploymentStatus) & !is.na(EmploymentStatusOther), 'Other', EmploymentStatus))
fcc$EmploymentStatus <- as.factor(fcc$EmploymentStatus)

# Change "NA" to "other" for EmploymentField if respondent provided EmploymentFieldOther
fcc$EmploymentField <- as.character(fcc$EmploymentField)
fcc$EmploymentField <- with(fcc, ifelse(is.na(EmploymentField) & !is.na(EmploymentFieldOther), 'other', EmploymentField))
fcc$EmploymentField <- as.factor(fcc$EmploymentField)

```

## Full Dataset
The original survey dataset consists of 113 variables. Most of these variables are answers to survey questions, though a few are computer-generated (e.g. respondent ID and survey start/end times). **Over 15,000 observations** (i.e. respondents) exist.

I created two new variables, *ContinentCitizen* and *ContinentLive*, for a new total of **115 variables**.

```{r echo=FALSE, Full_Dataset}
dim(fcc)
```

The [```str``` function](http://www.r-bloggers.com/str-implementation-for-data-frames/) output is long and messy, so I won't print it here. Please consult Free Code Camp's [list of survey questions and possible answers](https://github.com/FreeCodeCamp/2016-new-coder-survey/blob/master/survey-data-dictionary.md).

## Data Science Subset
646 respondents answered "*Data Scientist/Data Engineer*" to the question: "*Which one of these roles are you most interested in?*"

```{r echo=FALSE, Data_Science_Dataset}
# "Which one of these roles are you most interested in?"
fcc_data <- with(fcc, fcc[JobRoleInterest == '  Data Scientist / Data Engineer' & !is.na(JobRoleInterest), ])
dim(fcc_data)
```

## Univariate Plots Section
```{r echo=FALSE, Univariate_Plot_Functions}
# Order factor based on the survey's data science subset results (ascending)
order_factor <- function(fcc_data_var) {
  table(fcc_data_var)
  var_table <- table(fcc_data_var)
  var_levels <- names(var_table)[order(var_table)]
  return(factor(fcc_data_var, levels = var_levels))
}

# Pretty bar chart
nice_bar_plot <- function(col, question, num_answers, lab_size, lab_cut) {
  df <- as.data.frame(col)
  colnames(df)[1] <- "x"
  
  title.grob <- textGrob(
    label = paste(question, sep=" "),
    x = unit(0.3, "lines"), 
    y = unit(-0.3, "lines"),
    hjust = 0, vjust = 0,
    gp = gpar(fontsize = 16, fontface="bold", col="#02b3e4"))
  
  dfTab <- as.data.frame(table(df))
  colnames(dfTab)[1] <- "x"
  
  dfTab$lab <- 100 * dfTab$Freq / num_answers
  dfTab$lab <- ifelse(dfTab$lab >= lab_cut, sprintf("%1.1f%%", dfTab$lab), "")
  dfTab$lab <- as.character(dfTab$lab)
  
  plot <- ggplot(df) +
    geom_bar(aes(x), color="#02b3e4", fill="#02b3e4") +
    theme_minimal() +
    scale_x_discrete(drop=FALSE) +
    labs(title="", x=NULL, y=paste(as.character(num_answers), "out of 646 developing data scientists/engineers answered")) +
    theme(axis.text=element_text(size=10),
          axis.title.x=element_text(colour = "#02b3e4", margin=margin(15,0,9,0))) +
    geom_text(data=dfTab, aes(x=x,y=Freq,label=lab), hjust = 1,
              color="white", size=lab_size, fontface=2) +
    coord_flip()
  
  plot <- arrangeGrob(plot, top = title.grob)
  return(plot)
}
```

### Who Participated
CodeNewbie and Free Code Camp designed the survey, and dozens of coding-related organizations publicized it to their members.

Of the 646 developing data scientists/engineers who responded to the survey:

- 25% are women
- Their median age is 26
- They started programming an average of 16 months ago

```{r echo=FALSE, Who_Participated}
# Gender
table(fcc_data$Gender)['female'] / sum(table(fcc_data$Gender))

# Age
median(fcc_data$Age, na.rm = TRUE)

# MonthsProgramming
mean(fcc_data$MonthsProgramming, na.rm = TRUE)
```

### Learner Goals and Approaches
Nobody wants to freelance or start their own business. Compared to 40% for the full new coder survey, this is somewhat shocking.

```{r echo=FALSE, message=FALSE, JobPref}
# JobPref
fcc_data$JobPref <- order_factor(fcc_data$JobPref)
job_pref_na_rm <- with(fcc_data, fcc_data[!is.na(JobPref), ])
g_job_pref <- grid.arrange(nice_bar_plot(job_pref_na_rm$JobPref, "Would you prefer to...", nrow(job_pref_na_rm), 7, 0))
ggsave(file="JobPref.png", g_job_pref)
```

52% percent are already applying for jobs, or will start applying within the next year.

```{r echo=FALSE, message=FALSE, JobApplyWhen}
# JobApplyWhen
fcc_data$JobApplyWhen <- order_factor(fcc_data$JobApplyWhen)
job_apply_when_na_rm <- with(fcc_data, fcc_data[!is.na(JobApplyWhen), ])
g_job_apply_when <- grid.arrange(nice_bar_plot(job_apply_when_na_rm$JobApplyWhen, "When do you plan to start applying for jobs?", nrow(job_apply_when_na_rm), 7, 0))
ggsave(file="JobApplyWhen.png", g_job_apply_when)
```

Most of them want to work in an office, as opposed to remotely.

```{r echo=FALSE, message=FALSE, JobWherePref}
# JobWherePref
fcc_data$JobWherePref <- order_factor(fcc_data$JobWherePref)
job_where_pref_na_rm <- with(fcc_data, fcc_data[!is.na(JobWherePref), ])
g_job_where_pref <- grid.arrange(nice_bar_plot(job_where_pref_na_rm$JobWherePref, "Would you prefer to work...", nrow(job_where_pref_na_rm), 9, 0))
ggsave(file="JobWherePref.png", g_job_where_pref)
```

And a majority are willing to relocate.

```{r echo=FALSE, message=FALSE, JobRelocateYesNo}
# JobRelocateYesNo
fcc_data$JobRelocateYesNo <- order_factor(fcc_data$JobRelocateYesNo)
job_relo_na_rm <- with(fcc_data, fcc_data[!is.na(JobRelocateYesNo), ])
g_job_relo <- grid.arrange(nice_bar_plot(job_relo_na_rm$JobRelocateYesNo, "Are you willing to relocate for a job?", nrow(job_relo_na_rm), 11, 0))
ggsave(file="JobRelocateYesNo.png", g_job_relo)
```

Most of them have not yet attended any in-person coding events.

```{r echo=FALSE, message=FALSE, CodeEvent}
# LEARN TO USE LAZYEVAL TO MAKE A FUNCTION FOR THE NEXT THREE WRANGLING SEQUENCES (CodeEvent, Resource, Podcast) IN THE FUTURE

# CodeEvent
code_event_cols <- select(fcc_data, CodeEventBootcamp:CodeEventWorkshop)
code_event_cols$CodeEventOther <-
  ifelse(!is.na(code_event_cols$CodeEventOther),
         as.integer(1), NA)
code_event_cols$answered <-
  ifelse(rowSums(code_event_cols, na.rm = TRUE) != 0, 1, 0)
num_answers_code_event <- sum(code_event_cols[,'answered'])
code_event_sum <- code_event_cols %>% summarise_each(funs(sum(., na.rm=TRUE)))
code_event_sum_long <- gather(code_event_sum, event, num_yes, CodeEventBootcamp:CodeEventWorkshop) %>%
  arrange(desc(num_yes)) %>%
  mutate(event = str_sub(event, nchar("CodeEvent") + 1, -1))
code_event_factor <- as.data.frame(rep(code_event_sum_long$event,
                                       code_event_sum_long$num_yes))
colnames(code_event_factor) <- "event"
code_event_factor$event <- order_factor(code_event_factor$event)
g_code_event <- grid.arrange(nice_bar_plot(code_event_factor$event, "Which types of in-person coding events have you attended?", num_answers_code_event, 3.8, 2.9))
ggsave(file="CodeEvent.png", g_code_event)
```

On average, they use at least three different resources for learning.

```{r echo=FALSE, message=FALSE, Resource}
# Resource
# length(resource_factor$resource) / dim(fcc_data)[1]
# 3.543344
resource_cols <- select(fcc_data, ResourceBlogs:ResourceYouTube)
resource_cols$ResourceOther <- ifelse(!is.na(resource_cols$ResourceOther), as.integer(1), NA)
resource_cols$answered <- ifelse(rowSums(resource_cols, na.rm = TRUE) != 0, 1, 0)
num_answers_resource <- sum(resource_cols[,'answered'])
resource_sum <- resource_cols %>% summarise_each(funs(sum(., na.rm=TRUE)))
resource_sum_long <- gather(resource_sum, resource, num_yes, ResourceBlogs:ResourceYouTube) %>%
  arrange(desc(num_yes)) %>%
  mutate(resource = str_sub(resource, nchar("Resource") + 1, -1))
resource_factor <- as.data.frame(rep(resource_sum_long$resource,
                                       resource_sum_long$num_yes))
colnames(resource_factor) <- "resource"
resource_factor$resource <- order_factor(resource_factor$resource)
resource_factor_lim <- resource_factor %>% group_by(resource) %>% filter(n() > 4)
g_resource <- grid.arrange(nice_bar_plot(droplevels(resource_factor_lim$resource), "Which learning resources have you found helpful?", num_answers_resource, 4, 5))
ggsave(file="Resource.png", g_resource)
```

Less than 20% listen to coding-related podcasts. Partially Derivative, Becoming A Data Scientist, and Talking Machines are data science/machine learning-specific podcasts.

```{r echo=FALSE, message=FALSE, Podcast}
# Podcast
podcast_cols <- select(fcc_data, PodcastChangeLog:PodcastWebAhead)
podcast_cols$PodcastOther <- ifelse(!is.na(podcast_cols$PodcastOther), as.integer(1), NA)
podcast_cols$answered <- ifelse(rowSums(podcast_cols, na.rm = TRUE) != 0, 1, 0)
num_answers_podcast <- sum(podcast_cols[,'answered'])
podcast_sum <- podcast_cols %>% summarise_each(funs(sum(., na.rm=TRUE)))
podcast_sum_long <- gather(podcast_sum, podcast, num_yes, PodcastChangeLog:PodcastWebAhead) %>%
  arrange(desc(num_yes)) %>%
  mutate(podcast = str_sub(podcast, nchar("Podcast") + 1, -1))
podcast_factor <- as.data.frame(rep(podcast_sum_long$podcast,
                                       podcast_sum_long$num_yes))
colnames(podcast_factor) <- "podcast"
podcast_factor$podcast <- order_factor(podcast_factor$podcast)
g_podcast <- grid.arrange(nice_bar_plot(podcast_factor$podcast, "Which coding-related podcasts have you found helpful?", num_answers_podcast, 4.5, 7))
ggsave(file="podcast.png", g_podcast)
```

Only 11 of the 954 respondents that attended a bootcamp in the full new coder survey are developing data scientists/engineers.

```{r echo=FALSE, message=FALSE, Bootcamp}
# Bootcamp
fcc_data$BootcampName <- order_factor(fcc_data$BootcampName)
bootcamp_name_na_rm <- with(fcc_data, fcc_data[!is.na(BootcampName), ])
g_bootcamp_name <- grid.arrange(nice_bar_plot(droplevels(bootcamp_name_na_rm$BootcampName), "If you have attended a full-time coding bootcamp, which one?", nrow(bootcamp_name_na_rm), 6, 0))
ggsave(file="BootcampName.png", g_bootcamp_name)
```


### Demographics and Socioeconomics
They data science/engineering subset of the survey had respondents from 166 countries.

```{r echo=FALSE, message=FALSE, Country}
# CountryCitizen
# length(names(table(fcc_data$CountryCitizen)))
# 166
fcc_data$CountryCitizen <- order_factor(fcc_data$CountryCitizen)
country_citizen_na_rm <- with(fcc_data, fcc_data[!is.na(CountryCitizen), ])
country_citizen_na_rm_lim <- country_citizen_na_rm %>% group_by(CountryCitizen) %>% filter(n() > 4)
g_country_citizen <- grid.arrange(nice_bar_plot(droplevels(country_citizen_na_rm_lim$CountryCitizen), "Which country are you a citizen of?", nrow(country_citizen_na_rm), 3.3, 3))
ggsave(file="CountryCitizen.png", g_country_citizen)

# CountryLive
# fcc_data$CountryLive <- order_factor(fcc_data$CountryLive)
# country_live_na_rm <- with(fcc_data, fcc_data[!is.na(CountryLive), ])
# country_live_na_rm_lim <- country_live_na_rm %>% group_by(CountryLive) %>% filter(n() > 4)
# g_country_live <- grid.arrange(nice_bar_plot(droplevels(country_live_na_rm_lim$CountryLive), "Which country do you currently live in?", nrow(country_live_na_rm), 2.5, 3))
# ggsave(file="CountryLive.png", g_country_live)
```

More than 90% of respondents are from North America, Europe, and Asia.

```{r echo=FALSE, message=FALSE, Continent}
# ContinentCitizen
fcc_data$ContinentCitizen <- order_factor(fcc_data$ContinentCitizen)
continent_citizen_na_rm <- with(fcc_data, fcc_data[!is.na(ContinentCitizen), ])
g_continent_citizen <- grid.arrange(nice_bar_plot(droplevels(continent_citizen_na_rm$ContinentCitizen), "Which continent are you a citizen of?", nrow(continent_citizen_na_rm), 8, 4))
ggsave(file="ContinentCitizen.png", g_continent_citizen)
```

Their cities span a wide range of urbanization levels, with a distribution that is nearly identical to the full new coder survey.

```{r echo=FALSE, message=FALSE, CityPopulation}
# CityPopulation
fcc_data$CityPopulation <- order_factor(fcc_data$CityPopulation)
city_pop_na_rm <- with(fcc_data, fcc_data[!is.na(CityPopulation), ])
g_city_pop <- grid.arrange(nice_bar_plot(city_pop_na_rm$CityPopulation, "About how many people live in your city?", nrow(city_pop_na_rm), 9, 0))
ggsave(file="CityPopulation.png", g_city_pop)
```

Just under a quarter of respondents are ethnic minorities in their country.

```{r echo=FALSE, message=FALSE, IsEthnicMinority}
# Ethnic Minority
fcc_data$IsEthnicMinority <- order_factor(fcc_data$IsEthnicMinority)
ethnic_minority_na_rm <- with(fcc_data, fcc_data[!is.na(IsEthnicMinority), ])
g_ethnic_minority <- grid.arrange(nice_bar_plot(ethnic_minority_na_rm$IsEthnicMinority, "Are you an ethnic minority in your country?", nrow(ethnic_minority_na_rm), 11, 0))
ggsave(file="IsEthnicMinority.png", g_ethnic_minority)
```

And nearly half are non-native English speakers. They grew up speaking one of 148 languages.

```{r echo=FALSE, message=FALSE, LanguageAtHome}
# LanguageAtHome
# length(names(table(fcc_data$LanguageAtHome)))
# 148
fcc_data$LanguageAtHome <- order_factor(fcc_data$LanguageAtHome)
language_na_rm <- with(fcc_data, fcc_data[!is.na(LanguageAtHome), ])
language_na_rm_lim <- language_na_rm %>% group_by(LanguageAtHome) %>% filter(n() > 5)
g_language <- grid.arrange(nice_bar_plot(droplevels(language_na_rm_lim$LanguageAtHome), "Which language do you speak at home with your family?", nrow(language_na_rm), 3.5, 3.6))
ggsave(file="LanguageAtHome.png", g_language)
```

67% have earned at least a bachelor’s degree. Compared to 58% for the full new coder survey, the data science/engineering subset is more skewed towards graduate studies.

```{r echo=FALSE, message=FALSE, SchoolDegree}
# SchoolDegree
fcc_data$SchoolDegree <- order_factor(fcc_data$SchoolDegree)
school_degree_na_rm <- with(fcc_data, fcc_data[!is.na(SchoolDegree), ])
g_school_degree <- grid.arrange(nice_bar_plot(school_degree_na_rm$SchoolDegree, "What's the highest level of school you have completed?", nrow(school_degree_na_rm), 3.5, 4))
ggsave(file="SchoolDegree.png", g_school_degree)
```

They studied 425 different majors. Computer Science and Mathematics were the two most popular majors, and an additional 16% studied some form of engineering.

```{r echo=FALSE, message=FALSE, SchoolMajor}
# SchoolMajor
# length(names(table(fcc_data$SchoolMajor)))
# 425
fcc_data$SchoolMajor <- order_factor(fcc_data$SchoolMajor)
school_major_na_rm <- with(fcc_data, fcc_data[!is.na(SchoolMajor), ])
school_major_na_rm_lim <- school_major_na_rm %>% group_by(SchoolMajor) %>% filter(n() > 5)
g_school_major <- grid.arrange(nice_bar_plot(droplevels(school_major_na_rm_lim$SchoolMajor), "What was the main subject your studied in university?", nrow(school_major_na_rm), 3, 0))
ggsave(file="SchoolMajor.png", g_school_major)
```

Just over one half are currently working.

```{r echo=FALSE, message=FALSE, EmploymentStatus}
# EmploymentStatus
fcc_data$EmploymentStatus <- order_factor(fcc_data$EmploymentStatus)
employment_status_na_rm <- with(fcc_data, fcc_data[!is.na(EmploymentStatus), ])
g_employment_status <- grid.arrange(nice_bar_plot(employment_status_na_rm$EmploymentStatus, "Regarding employment status, are you currently...", nrow(employment_status_na_rm), 6, 8))
ggsave(file="EmploymentStatus.png", g_employment_status)
```

Employment fields are more spread compared to the full new coder survey, where 50% of respondents work in software development and IT.

```{r echo=FALSE, message=FALSE, EmploymentField}
# EmploymentField
fcc_data$EmploymentField <- order_factor(fcc_data$EmploymentField)
employment_field_na_rm <- with(fcc_data, fcc_data[!is.na(EmploymentField), ])
g_employment_field <- grid.arrange(nice_bar_plot(droplevels(employment_field_na_rm$EmploymentField), "Which field do you work in?", nrow(employment_field_na_rm), 4, 2))
ggsave(file="EmploymentField.png", g_employment_field)
```

## Univariate Analysis

# Change levels 0 > no, 1>yes for fcc and not fcc_data?

#### What is the structure of your dataset?

#### What is/are the main feature(s) of interest in your dataset?

#### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?

#### Did you create any new variables from existing variables in the dataset?

#### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?



## Bivariate Plots Section
```{r echo=FALSE, Bivariate_Plots}

```

## Bivariate Analysis

#### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

#### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

#### What was the strongest relationship you found?




## Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

```

## Multivariate Analysis

#### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

#### Were there any interesting or surprising interactions between features?

#### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

------

## Final Plots and Summary

#### Plot One
```{r echo=FALSE, Plot_One}

```

#### Description One


#### Plot Two
```{r echo=FALSE, Plot_Two}

```

#### Description Two


#### Plot Three
```{r echo=FALSE, Plot_Three}

```

#### Description Three

------

## Reflection
