# Developing Data Scientists: Exploring Free Code Camp's ["2016 New Coder Survey"](https://www.kaggle.com/freecodecamp/2016-new-coder-survey-)
#### By [David Venturi](http://davidventuri.com/)

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(countrycode)
library(dplyr)
library(ggthemes)
library(scales)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
setwd('~/Documents/CS/DAND/udacity-dand/p4')
fcc <- read.csv('2016-FCC-New-Coders-Survey-Data.csv')

# Create new continent variables and move them to their alphabetical position
fcc$ContinentCitizen <- countrycode(fcc$CountryCitizen, 'country.name', 'continent')
fcc$ContinentLive <- countrycode(fcc$CountryLive, 'country.name', 'continent')
fcc <- subset(fcc, select = c(Age:CountryCitizen, ContinentCitizen, CountryLive, ContinentLive, EmploymentField:StudentDebtOwe))

# 66 countries with no assigned continent via countrycode()
cit_live_cols <- subset(fcc, select = c(CountryCitizen:ContinentLive))
problem_countries <- subset(cit_live_cols, (!is.na(fcc$CountryCitizen) & is.na(fcc$ContinentCitizen) | !is.na(fcc$CountryLive) & is.na(fcc$ContinentLive)))

# Problem country/continent names
fix_cont <- c('Africa', 'Asia', 'Europe', 'Europe', 'Europe', 'Oceania')
names(fix_cont) <- c('Nambia', 'Taiwan', 'Canary Islands', 'Kosovo', 'Channel Islands', 'Hawaii')
# "Hawaii is generally included in Oceania, even though it is a part of the United States" http://cs.mcgill.ca/~rwest/wikispeedia/wpcd/wp/o/Oceania.htm

# Assign continents to problem countries
fcc$ContinentCitizen <- ifelse(fcc$CountryCitizen %in% names(fix_cont), fix_cont[as.character(fcc$CountryCitizen)], fcc$ContinentCitizen)
fcc$ContinentLive <- ifelse(fcc$CountryLive %in% names(fix_cont), fix_cont[as.character(fcc$CountryLive)], fcc$ContinentLive)

# South American countries in dataset
s_america <- c('Argentina', 'Bolivia', 'Brazil', 'Chile', 'Colombia', 'Ecuador', 'Guyana', 'Netherland Antilles', 'Paraguay', 'Peru', 'Uruguay', 'Venezuela')

# Separate Americas into North and South
make_s_america <- function(continent, country) {
  return(ifelse(continent == 'Americas' & country %in% s_america, 'South America', continent))
}

make_n_america <- function(continent, country) {
  return(ifelse(continent == 'Americas' & !(country %in% s_america), 'North America', continent))
}

fcc$ContinentCitizen <- make_s_america(fcc$ContinentCitizen, fcc$CountryCitizen)
fcc$ContinentCitizen <- make_n_america(fcc$ContinentCitizen, fcc$CountryCitizen)
fcc$ContinentLive <- make_s_america(fcc$ContinentLive, fcc$CountryLive)
fcc$ContinentLive <- make_n_america(fcc$ContinentLive, fcc$CountryLive)

# TEST
# table(fcc$ContinentLive)
# table(fcc$ContinentCitizen)

# Make continents factor variables
fcc$ContinentCitizen <- factor(fcc$ContinentCitizen)
fcc$ContinentLive <- factor(fcc$ContinentLive)
```

## Full Dataset
The original survey dataset consists of 113 variables. Most of these variables are answers to survey questions, though a few are computer-generated (e.g. respondent ID and survey start/end times). **Over 15,000 observations** (i.e. respondents) exist.

I created two new variables, *ContinentCitizen* and *ContinentLive*, for a new total of **115 variables**.

```{r echo=FALSE, Full_Dataset}
dim(fcc)
```

The [```str``` function](http://www.r-bloggers.com/str-implementation-for-data-frames/) output is long and messy, so I won't print it here. Please consult Free Code Camp's [list of survey questions and possible answers](https://github.com/FreeCodeCamp/2016-new-coder-survey/blob/master/survey-data-dictionary.md).

## Data Science Subset
646 respondents answered "*Data Scientist/Data Engineer*" to the question: "*Which one of these roles are you most interested in?*"

```{r echo=FALSE, DS_Dataset}
# "Which one of these roles are you most interested in?"
fcc_data <- subset(fcc, JobRoleInterest == '  Data Scientist / Data Engineer')
dim(fcc_data)
```

## Univariate Plots Section
```{r echo=FALSE, Univariate_Plots}
# Histograms, Frequency Polygons, Boxplots

# Learner goals and approaches
table(fcc_data$JobPref)
JobPref_table <- table(fcc_data$JobPref)
JobPref_levels <- names(JobPref_table)[order(JobPref_table)]
fcc_data$JobPref <- factor(fcc_data$JobPref, levels = JobPref_levels)

ggplot(aes(x=JobPref, fill=JobPref), data = subset(fcc_data, !is.na(fcc_data$JobPref))) +
  geom_bar() +
  scale_x_discrete(drop=FALSE) +
  scale_fill_discrete(name="Job Preference", drop=FALSE, guide = guide_legend(reverse=TRUE)) +
  labs(title = "Would you prefer to...", y = "641 out of 646 developing data scientists/engineers answered this question") +
  coord_flip() +
  scale_y_continuous() +
  theme(axis.title.y=element_blank(), axis.title.x=element_text(size=8.5)) +
  geom_text(aes(label = sprintf("%1.1f%%", ..count../sum(..count..)*100)), stat="count", hjust = 1.25, color="white")
```

## Univariate Analysis

#### What is the structure of your dataset?

#### What is/are the main feature(s) of interest in your dataset?

#### What other features in the dataset do you think will help support your investigation into your feature(s) of interest?

#### Did you create any new variables from existing variables in the dataset?

#### Of the features you investigated, were there any unusual distributions? Did you perform any operations on the data to tidy, adjust, or change the form of the data? If so, why did you do this?



## Bivariate Plots Section
```{r echo=FALSE, Bivariate_Plots}

```

## Bivariate Analysis

#### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

#### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

#### What was the strongest relationship you found?




## Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

```

## Multivariate Analysis

#### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

#### Were there any interesting or surprising interactions between features?

#### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

------

## Final Plots and Summary

#### Plot One
```{r echo=FALSE, Plot_One}

```

#### Description One


#### Plot Two
```{r echo=FALSE, Plot_Two}

```

#### Description Two


#### Plot Three
```{r echo=FALSE, Plot_Three}

```

#### Description Three

------

## Reflection
